%-------------------------------------------------------------------------------
% File: requirements.tex
%       Part of StockSim project documentation.
%       See main.tex for further information.
%-------------------------------------------------------------------------------
\chapter{Actors and requirements}
The main actors and the functional requirements can be defined using the simple
application description provided in the introductory chapter. Non-functional
requirements, described in detail in the second section of this chapter, are the
characteristics that ensure satisfactory interaction with users and real world
utility of the product.

\section{Actors}
Based on the application design, four main actors can be identified:
\begin{itemize}
    \item A \textbf{Guest user} is someone who is not yet registered (does not
    have a valid account to be able to use the application); this actor does not
    own private credentials for the login; in order to exploit the application
    main functionalities, he must register a new user account; therefore, the
    registration is the only action allowed for a Guest;

    \item A \textbf{Registered user} is someone who sign up on the application;
    this actor owns private credentials (username and password) for the login;
    he can login as a user into the client application and utilize its main
    features to watch stocks information, compose portfolios and simulate them. 
   
    \item An \textbf{Admin user} is someone who is registered on the application
    with administration credentials; this actor can login as an admin into the
    client to perform maintenance operations; these operations include, among
    others, checking the integrity of the entire database and add new stocks to
    it;

    \item The \textbf{Data Updater} is a thread running on StockSim Server; this 
    thread is supposed to be always running, and it is in charge of updating the
    database historical data with the new information coming from the stock
    market daily trading sessions; it is also in charge of finding and fixing
    (or at least report) integrity issues.
\end{itemize}
Please refer to Chapter 3 for the full use case diagram.

\section{Requirements}

\subsection{Functional requirements}
\begin{itemize}
	\item The user, upon launching the application, should be able to sign-up and sign-in.
	\item The user should be able to search for a stock and view related details.
	\item The user should be able to view charts of the historical data of a stock.
	\item The user should be able to create and delete portfolios.
	\item The user should be able to add/remove stocks to/from their portfolio.
	\item The user should be able to run simulations on a portfolio.
	\item The user should be able to visualize statistics about a simulation and possibly view related charts.
	\item Only admins should be able to add new stocks to the database.
	\item Only admins should be able to create new admin accounts.
	\item Only admins should be able to delete admin accounts.
	\item Only admins should be able to delete user accounts.
	\item The software should always provide the most recent data available for a stock.
\end{itemize}

\subsection{Non-functional requirements}
\begin{itemize}
	\item The retrieval of data about stocks and portfolios should be fast.
	\item User password should be stored in a secure way (i.e. hashed).
\end{itemize}
